Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Modular Forms.

@@

These are our results.
\begin{thm}
\label{thm:general_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx,
\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta
, \halfcan)$ has relations in degree at most $\max(10, e_1, \ldots,
e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
for signatures with $g = 0$.
\end{thm}

Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].

>>>>

\section{Introduction}

@@

\begin{thm}
\label{thm:general_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\noindent
is generated as a $k$-algebra by elements of degree at most $e =
\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx,
\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta
, \halfcan)$ has relations in degree at most $\max(10, e_1, \ldots,
e_r),$ so long as $\sigma$ does not lie in a finite list of
exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
for signatures with $g = 0$.
\end{thm}
\todo{Say that this follows immediately from the three theorems for the special cases.}
Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations. In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations. While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$. In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].
